Deterministic and statistical truncated KdV models for anomalous waves induced by abrupt depth change

### 2018-09-26 LatexNotes/Notes.tex
NM

\subsubsection{Johnson's formulation}
Following Johnson's derivation the dimensionless KdV equation is (on page 208)
\begin{equation}
2 \eta_{\tau} + 3 \eta \eta_{\xi} + \frac{1}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
I had to work backwards quite a bit to figure out how this was non-dimensionalized (Johnson keeps rescaling things over and over again). Ultimately, the characteristic scales are
\begin{align}
& Z^* = h_0 , \quad X^* = \eps^{-1/2} h_0 , \quad T^* = \eps^{-1/2} \sqrt{h_0/g} , \\
& W^* = \eps^{3/2} \sqrt{g h_0} , \quad U^* = \eps \sqrt{g h_0} , \quad P^* = \eps \rho g h_0
\end{align}
where $\eps$ is the ratio of characteristic amplitude to depth
\begin{equation}
\eps = a / h_0
\end{equation}
The variables $\tau$ and $\xi$ are
\begin{align}
\tau = \eps t , \quad \xi = x-t
\end{align}
Remember, the privileged KdV scaling is $\delta^2 \sim \eps$ where $\delta = h_0 / \lambda$. If this scaling is inserted into above, then $X^* \sim \lambda$, $T^* \sim \lambda/\sqrt{g h_0}$ which all makes sense.

@@

>>>>

\subsubsection{Johnson's formulation}
Following Johnson's derivation, the dimensionless KdV equation is (on page 208)
\begin{equation}
2 \eta_{\tau} + 3 \eta \eta_{\xi} + \frac{1}{3} \eta_{\xi \xi \xi} = 0
\end{equation}
I had to work backwards quite a bit to figure out how this was non-dimensionalized (Johnson keeps rescaling things over and over again). Ultimately, the characteristic scales are
\begin{align}
& X^* = \eps^{-1/2} h_0 ,\quad T^* = \eps^{-1/2} \sqrt{h_0/g} , \quad \eta^* = \eps h_0, \\
& Z^* = h_0 , \quad U^* = \eps \sqrt{g h_0} , \quad W^* = \eps^{3/2} \sqrt{g h_0} , \quad P^* = \eps \rho g h_0
\end{align}
where $\eps$ is the ratio of characteristic amplitude to depth
\begin{equation}
\eps = a / h_0
\end{equation}
The variables $\tau$ and $\xi$ are
\begin{align}
\tau = \eps t , \quad \xi = x-t
\end{align}
Remember, the privileged KdV scaling is $\delta^2 \sim \eps$ where $\delta = h_0 / \lambda$. If this scaling is inserted into above, then $X^* \sim \lambda$, $T^* \sim \lambda/\sqrt{g h_0}$ which all makes sense.

@@

\subsubsection{Reformulating variable-depth KdV}

We now seek to formulate the variable-depth KdV in a similar fashion. We start with Johnson's Eq. (3.148), which is written in dimensionless variables
\begin{equation}
2 \sqrt{D} \eta_X + \frac{1}{2} \frac{D'(X)}{\sqrt{D}} \eta + \frac{3}{D} \eta \eta_\xi + \frac{1}{3} D \eta_{\xi \xi \xi} = 0
\end{equation}
The first task is to convert this to dimensional form. For this, we now denote dimensionless variables with a tilde and use the relationships
\begin{align}
\eta = \eps h_0 \tilde{\eta} , \quad x = \eps^{-1/2} h_0 \tilde{x} = \eps^{-3/2} h_0 \tilde{X}
\end{align}
The trickiest part relates to $\xi$.
